Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/approach.tex
Some Changes

\begin{figure}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
    Integer a := 1
    Integer b := 2
    send ( a + '_' + b )
    recv (buf)
    Integer result := parse (buf)
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
    recv (buf)
    Integer first := getFirstOperand( buf )
    Integer second := getSecondOperand( buf )
    Integer sum := first + second
    send ( sum )
\end{lstlisting}
\end{minipage}\hfill
\end{figure}

@@

Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
\begin{itemize}
\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be collected at each point is determined
\item Program is instrumented to log selected variable values, their type and current vector clock at the annotated program points at run time
\item Program is executed by test cases or appropriate inputs and logs of variables are collected
\item Based on the vector clock of each log, logs are paired to each other
\item Combined variable values of two logs is fed to the daikon in its specific format.
%For this we are hoping to use static analysis libraries
%available under Go-lang Parse package and tools\cite{static_golang} which provide
%support for Identifier resolution, Type information, Call graph
%navigation and Channel peers (send $\leftrightarrow$ receive)
%identification.
%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
%\item Forward flow analysis is done on the collected traces
%\item Using the results of the previous step, variables contributing to distributed state is identified.
%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
\end{itemize}
In each of the following sections we explain each step in detail.
\begin{figure}
  \includegraphics[width=\columnwidth]{go_flow.png}
  \caption{Flow of the invariant inference of Go programs}
  \label{fig:go_flow}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth,scale=0.5]{images/PDG-approach.png}
  \caption{Our approach to compute program dependence graph}
  \label{fig:pdg}
\end{figure}

@@

\subsection{Matching Logs with Vector Clocks}

>>>>

\begin{figure}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
    a := 1
    b := 2
    send ( a + '_' + b )
    recv (buf)
    Integer result := parse (buf)
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
    recv (buf)
    first := getFirstOperand( buf )
    second := getSecondOperand( buf )
    sum := first + second
    send ( sum )
\end{lstlisting}
\end{minipage}\hfill
\caption{An example program}
\label{fig:exampleprog}
\end{figure}

@@

Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
\begin{itemize}
\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be collected at each point is determined
\item Program is instrumented to log selected variable values, their type and current vector clock at the annotated program points at run time
\item Program is executed by test cases or appropriate inputs and logs of variables are collected
\item Based on the vector clock of each log, logs are paired to each other
\item Combined variable values of two logs is fed to the daikon in its specific format.
%For this we are hoping to use static analysis libraries
%available under Go-lang Parse package and tools\cite{static_golang} which provide
%support for Identifier resolution, Type information, Call graph
%navigation and Channel peers (send $\leftrightarrow$ receive)
%identification.
%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
%\item Forward flow analysis is done on the collected traces
%\item Using the results of the previous step, variables contributing to distributed state is identified.
%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
\end{itemize}
In each of the following sections we explain each step in detail.
\begin{figure}
  \includegraphics[width=\columnwidth]{go_flow.pdf}
  \caption{Flow of the invariant inference of Go programs}
  \label{fig:go_flow}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[scale=0.3]{images/PDG-approach.png}
  \caption{Our approach to compute program dependence graph}
  \label{fig:pdg}
\end{figure}

@@

\subsection{Matching Logs with Vector Clocks and Feeding to Invariant Detector}

Having the set of distributed state variables at each annotated point in the program by control and data flow analysis, we instrument the program so as to log these variables at the specified points. While logging variables, we also log the vector clock at the annotated point, this help us to match immediate logs across two nodes with each other and merge the logs and make a global snapshot of the system to form a consistent cut. We also log the type of each variable, so we can recover these variables from log file. Then, we convert each merged log to the specific format to be used as input for Daikon invariant detector and run the Daikon.

### 2015-05-01 Doc/evalrelate.tex
Some Changes

\subsection{Implementation}

\subsubsection{Program Slicer}

@@

\section{Results}
We will implement our approach in a tool in Go programming language. We plan to evaluate our tool by verifying correctness of two-phase commit and leader election protocols. Our tool should be able to infer safety property of both algorithms. In two-phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property. In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property). It is worth mentioning that our approach is not suitable for checking the liveness properties of these algorithms.

@@

\section{Acknowledgment}
We would like to thank Ivan Beschastnikh for his valuable insight and feedback on initial draft of this proposal.

>>>>

\section{Implementation Details}

In this section we explain the details of prototype of our approach implemented in Go programming language.

\subsection{Program Slicer}

@@

\section{Evaluation}
We implemented our approach in a tool in Go programming language. We evaluated our tool by verifying correctness of pseudo-two-phase commit of figure \ref{lst:2pc} and example program of figure \ref{fig:exampleprog}. Our tool was able to infer the expected invariants in both of these programs. Also, different components of our tool such as program slicer, instrumenter and log merger have been tested in isolation to ensure correctness of the prototype. It is worth mentioning, that our prototype currently only handles scalar variables but extending it to handle structs is only an extra engineering effort. %We also do not perform interprocedural data and control flow analysis, so we always log all global variables and

@@

\section{Acknowledgment}
We would like to thank Ivan Beschastnikh for his valuable insight and feedback on proposal of this project.
